TBD

### 2016-10-13 paper.tex
improved CG section

\subsection{Preconditioning}
Preconditioning is a technique which allows us to improve the condition number of a matrix. Let $\bM$ be a positive-definite Hermitian matrix which approximates $\bA$.
Moreover, the inverse of $\bM$ must also be much easier to compute than the inverse of $\bA$. We can now indirectly solve for $\bx$ by using 
\begin{equation}
\label{eq:prec}
\bM^{-1}\bA\bx = \bM^{-1}\bb.
\end{equation}
The logic behind using Eq.~\eqref{eq:prec} rather than Eq.~\eqref{eq:linear_system} to obtain $\bx$ is that if $\bM$ is a good preconditioner then $\kappa(\bM^{-1}\bA) \ll \kappa(\bA)$, i.e.
by preconditioning we reduce $\kappa$ which improves the convergence rate of CG. The best choice of $\bM$ would be $\bA$, which would reduce $\kappa$ to unity which reduces
Eq.~\eqref{eq:cg_bound} to $\mathbb{O}(m)$. But of course, if we knew the inverse of $\bA$ then obtaining $\bx$ would be trivial and we would not need CG or any other type of 
linear solver for that mattter to compute it in the first place. If the diagonal entries of $\bA$ is much more significant than its off-diagonal entries then the 
Jacobian preconditioner is a good choice of $\bM$. The Jacobian preconditioner is computed as follows:
\begin{equation}
\bM = \bA\odot\bI, 
\end{equation}
where $\bI$ is the identity matrix. Since the Jacobian preconditioner is a diagonal matrix is inverse can be computed trivially.

>>>>

\subsection{Preconditioning}
Preconditioning is a technique which allows us to improve the condition number of a matrix. Let $\bM$ be a positive-definite Hermitian matrix which approximates $\bA$.
Moreover, the inverse of $\bM$ must also be much easier to compute than the inverse of $\bA$. We can now indirectly solve for $\bx$ by using 
\begin{equation}
\label{eq:prec}
\bM^{-1}\bA\bx = \bM^{-1}\bb.
\end{equation}
The logic behind using Eq.~\eqref{eq:prec} rather than Eq.~\eqref{eq:linear_system} to obtain $\bx$ is that if $\bM$ is a good preconditioner then $\kappa(\bM^{-1}\bA) \ll \kappa(\bA)$, i.e.
by preconditioning we reduce $\kappa$ which improves the convergence rate of CG. The best choice of $\bM$ would be $\bA$, which would reduce $\kappa$ (as the largest and smallest eignevalue of the Identity matrix is equal to one) to unity which reduces
Eq.~\eqref{eq:cg_bound} to $\mathbb{O}(m)$. But of course, if we knew the inverse of $\bA$ then obtaining $\bx$ would be trivial and there would be no need for the CG method in the first place. 
The better $\bM$ approximates $\bA$ the better preconditioner it will be. However, if it is not much less expensive to 
compute the inverse of $\bM$ thant that of $\bA$ we gain nothing, as we still need to

If the diagonal entries of $\bA$ is much more significant than its off-diagonal entries then the 
Jacobian preconditioner is a good choice of $\bM$. The Jacobian preconditioner is computed as follows:
\begin{equation}
\bM = \bA\odot\bI, 
\end{equation}
where $\bI$ is the identity matrix. Since the Jacobian preconditioner is a diagonal matrix is inverse can be computed trivially.
